Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-04-06 paperICSME.tex
añadiendo comentarios sobre related work
Añadiendo una referencia related work

\gema{Añadir algunas referencias que nos comentaron los revisores: (Kamei et al., "A Large-Scale Empirical Study of Just-in-Time Quality Assurance," TSE 2013
Tan et al., "Online Defect Prediction for Imbalanced Data," ICSE SEIP 2015
Tantithamthavorn et al., "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models," ICSE 2015)}
\gema{A brief summary about "A Large-Scale Empirical Study of Just-in-Time Quality Assurance": In this paper the concept of 'Just-in Time Quality Assurance' is presented, this concept focus in identifying defect-prone at level of software changes/patches instead of files or packages, this way the developers can review these risky changes while they are still fresh in their minds. In the paper they present as change risk model in which several characteristics of a software changes are implemented(lines added, developer experience...) They want provide an effort-reducing way to focus on the most risky changes, they empirically evaluated their approach in "Just-In-Time Quality Assurance" to identify in real time software changes that would be a defect}

\gema{A brief summary about "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models": In the paper the authors carried out a study where investigated the nature of mislabelled issue reports and also how this mislabelled impact in the prediction models. Finding that the mislabelling is not random. Furthermore the models trained using data noise are often just as accurate as the ones trained with clear data, but using clear data will likely allow the models to identify more of the truly defective modules. }

\gema{{A brief summary about "Online Defect Prediction for Imbalanced Data":  }

>>>>

\gema{Añadir algunas referencias que nos comentaron los revisores: (Kamei et al., "A Large-Scale Empirical Study of Just-in-Time Quality Assurance," TSE 2013
Tan et al., "Online Defect Prediction for Imbalanced Data," ICSE SEIP 2015
Tantithamthavorn et al., "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models," ICSE 2015)}

~\cite{kamei2013large} 
\gema{A brief summary about "A Large-Scale Empirical Study of Just-in-Time Quality Assurance": In this paper the concept of 'Just-in Time Quality Assurance' is presented, this concept focus in identifying defect-prone at level of software changes/patches instead of files or packages, this way the developers can review these risky changes while they are still fresh in their minds. In the paper they present as change risk model in which several characteristics of a software changes are implemented(lines added, developer experience...) They want provide an effort-reducing way to focus on the most risky changes, they empirically evaluated their approach in "Just-In-Time Quality Assurance" to identify in real time software changes that would be a defect}

~\cite{tantithamthavorn2015impact} 
\gema{A brief summary about "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models", \cite{tantithamthavorn2015impact}: In the paper the authors carried out a study where investigated the nature of mislabelled issue reports and also how this mislabelled impact in the prediction models. Finding that the mislabelling is not random. Furthermore the models trained using data noise are often just as accurate as the ones trained with clear data, but using clear data will likely allow the models to identify more of the truly defective modules. }

~\cite{altman1968financial} 
\gema{A brief summary about "Online Defect Prediction for Imbalanced Data",\cite{altman1968financial}: A change classification can predict whether a change is buggy at the time of the commit, which allow to developers to act on the prediction results as soon as a commit is made, the benefit is that reviewers have less code to examine to identify defect, but the problem is that for the same reason is more difficult to predict on changes accurately. The authors applied change classification on a proprietary code case and share the experience and lesson learned. They evaluated the change classification techniques to address the incorrect evaluation presented by cross-validation, and applied some techniques improving the precision, they conclude that interpretable prediction models  are needed for software defect prediction, They used the SZZ approach saying that 'A line that is deleted or changed by a bug-fixing change is a faulty line'}
